```{r}
library(forecast)
library(ggplot2)
library(xlsx)
library(fpp2)
```



# Importing the Power Data
We load the data and plot them:
```{r}
all_data <- read.xlsx("/Users/tim/Library/CloudStorage/OneDrive-DataScienceTechInstitute/Time Series Analysis (Big Coeff)/Exam/Elec-train.xlsx", sheetIndex=1, header=TRUE)

train_test_data <- all_data[1:4603,]

# We make a hour unit instead of a 15min unit
elec <- ts(train_test_data$Power..kW., start=c(1,2), freq=4)
autoplot(elec) +
  ggtitle("Electrecity consumption") +
  xlab("Time (hours)") +
  ylab("Electricity (KW)")
```
There seems to be no trend, but a "seasonal pattern" visible for each day.



Some stats about the elec time series:
```{r}
summary(elec)
```



```{r}
# Train = 80% of the train_test_data = 4603 * 0.8 = 3682 observations
elec_train <- window(elec,end=c(921,3))
# Test = 20% of the train_test_data = 4603 - 3682 = 921 observations
elec_test <- window(elec, start=c(921,4))
```



## SES & Holt Winters models
```{r}
# SES model
SES_fit <- ses(elec_train, h=921, alpha=NULL)

# non-Seasonal Holt Winters model
nsHW_fit <- holt(elec_train, h=921, alpha=NULL, beta=NULL)

# Additive Seasonal Holt Winters model
ASHW_fit <- hw(elec_train, seasonal="additive", h=921)

# Additive Seasonal Holt Winters model (Damped)
ASHW_D_fit <- hw(elec_train, seasonal="additive", h=921, damped=TRUE)

# Multiplicative Seasonal Holt Winters model
MSHW_fit <- hw(elec_train, seasonal="multiplicative", h=921)

# Multiplicative Seasonal Holt Winters model (Damped)
MSHW_D_fit <- hw(elec_train,
                    seasonal="multiplicative",
                    h=921,
                    damped=TRUE)
```



```{r}
message("RMSE SES_fit : ", sqrt(mean((SES_fit$mean-elec_test)^2)))
message("RMSE nsHW_fit : ", sqrt(mean((nsHW_fit$mean-elec_test)^2)))
message("RMSE ASHW_fit : ", sqrt(mean((ASHW_fit$mean-elec_test)^2)))
message("RMSE ASHW_D_fit : ", sqrt(mean((ASHW_D_fit$mean-elec_test)^2)))
message("RMSE MSHW_fit : ", sqrt(mean((MSHW_fit$mean-elec_test)^2)))
message("RMSE MSHW_D_fit : ", sqrt(mean((MSHW_D_fit$mean-elec_test)^2)))
```
The Multiplicative Seasonal HW fit seems to be very bad.
The best model is the SES, as it's error is the lowest one.



lets plot the models:
```{r}
autoplot(elec_train, series = "Train") + 
  autolayer(elec_test, series = "Test") +
  autolayer(SES_fit$mean, series = "SES") +
  autolayer(nsHW_fit$mean, series = "non-Seasonal HW") +
  autolayer(ASHW_fit$mean, series = "Additive Seasonal HW") +
  autolayer(ASHW_D_fit$mean, series = "Additive Seasonal HW Damped") +
  # autolayer(MSHW_fit$mean, series = "Multiplicative Seasonal HW") +
  autolayer(MSHW_D_fit$mean, series = "Multiplicative Seasonal HW Damped") +
  ggtitle("Electricity consumption") +
  xlab("Time (hour)") +
  ylab("Electricity (kW)") +
  xlim(c(500,1200))
```
The MSHW is removed from the graph, the model being too bad to be plotted.



## Auto SARIMA model
```{r}
SARIMA_fit <- auto.arima(elec_train)
Predict_SARIMA <- forecast(SARIMA_fit, h=921)

autoplot(elec_train, series = "Train") + 
  autolayer(elec_test, series = "Test") +
  autolayer(Predict_SARIMA, series = "SARIMA", PI=FALSE) +
  ggtitle("Electricity Consumption") +
  xlab("Time (hour)") +
  ylab("Electricity (kW)") +
  xlim(c(850,1200))
```
The SARIMA is starting to follow the pattern aspect of the curve, it looks better than the previous models.



Lets compute the RMSE
```{r}
message("RMSE Predict_SARIMA : ", sqrt(mean((Predict_SARIMA$mean-elec_test)^2)))
```
The SARIMA RMSE (57.2087133995781) is indeed better than the previous models !
A lower RMSE could be reached by investigating the ACF and PACF and testing different parameters for p,d and q.



## Auto NNAR model
```{r}
NN_fit <- nnetar(elec_train)
Predict_NN <- forecast(NN_fit, h=921)

autoplot(elec_train, series = "Train") + 
  autolayer(elec_test, series = "Test") +
  autolayer(Predict_NN$mean, series = "NNAR") +
  ggtitle("Electricity Consumption") +
  xlab("Time (hour)") +
  ylab("Electricity (kW)") +
  xlim(c(850,1200))
```
The NNAR model follows pretty much the pattern of the curve !



Lets compute the RMSE
```{r}
message("RMSE Predict_NN : ", sqrt(mean((Predict_NN$mean-elec_test)^2)))
```
The NNAR model (RMSE: 79.8714650815262) does not do better than the SARIMA model, despite the prediction pattern being better than the SARIMA's ...



## Making the predictions w/o the temperatures
96 observations are to be predicted from the original dataset
```{r}
SARIMA_final_fit <- auto.arima(elec)
Predict_SARIMA_final <- forecast(SARIMA_final_fit, h=96)

autoplot(elec, series = "Electricity Consumption Datas") + 
  autolayer(Predict_SARIMA_final$mean, series = "Electricity Consumption SARIMA Predictions") +
  ggtitle("Electricity Consumption") +
  xlab("Time (hour)") +
  ylab("Electricity (kW)") +
  xlim(c(850,1200))
```



Exporting the predictions:
```{r}
Predict_SARIMA_final$mean
write.xlsx(Predict_SARIMA_final$mean, "/Users/tim/Library/CloudStorage/OneDrive-DataScienceTechInstitute/Time Series Analysis (Big Coeff)/Exam/preds.xlsx", sheetName = "Sheet1", col.names = TRUE, row.names = FALSE, append = FALSE)
```



# Importing the Temperature Data
```{r}
# We make a hour unit instead of a 15min unit
temp <- ts(train_test_data$Temp..C.., start=c(1,2), freq=4)
autoplot(temp) +
  ggtitle("Temperature plot") +
  xlab("Time (hour)") +
  ylab("Temperature (°C)")
```



```{r}
# Train = 80% of the train_test_data = 4603 * 0.8 = 3682 observations
temp_train <- window(temp,end=c(921,3))
# Test = 20% of the train_test_data = 4603 - 3682 = 921 observations
temp_test <- window(temp, start=c(921,4))
```



## Linear regression model
Lets build a linear model with the temperature to see its impact on the power consumption:
```{r}
LM_fit <- tslm(elec_train ~ temp_train)
summary(LM_fit)
```
The p-value of the temperature is <<< 0.05.
It is then highly correlated with the power consumption.



Lets try to add a trend and a season pattern to this linear model:
```{r}
LM_fit_TS <- tslm(elec_train ~ temp_train + trend + season)
summary(LM_fit_TS)
```
Only the trend seem to have an impact on the power consumption.



Lets try to add only a trend to the linear model:
```{r}
LM_fit_T <- tslm(elec_train ~ temp_train + trend)
summary(LM_fit_T)
```
It seems a nice model, all p-values are <<< 0.05.



We can compare the previous models to see their metrics:
```{r}
print("Metrics for LM_fit: ")
CV(LM_fit)

print("Metrics for LM_fit_TS: ")
CV(LM_fit_TS)

print("Metrics for LM_fit_T: ")
CV(LM_fit_T)
```
We can see that the last model (temperature + trend) has the best metrics everywhere (Lowest CV, AIC, AICc, BIC and highest AdjR2).


To use it, we have to check if the residuals are independant.
```{r}
checkresiduals(LM_fit_T, test="LB", plot=TRUE)
```
The p-value is <<< 0.05, so we have to use another model, like an ARIMA model



## Auto Arima model
```{r}
NNAR_temp_fit <- auto.arima(elec_train, xreg = temp_train)
summary(NNAR_temp_fit)
```



Residuals check:
```{r}
checkresiduals(NNAR_temp_fit, test="LB", plot=TRUE)
```
The ARIMA p-value is > 0.05, so the residuals are independant, we can use this model !



```{r}
Predict_ARIMA <- forecast(NNAR_temp_fit, xreg = temp_test, h = 921)

autoplot(elec_train, series = "Train") +
  autolayer(elec_test, series = "Test") +
  autolayer(Predict_ARIMA, series = "ARIMA w/ temperature", PI=FALSE) +
  ggtitle("Electricity Consumption") +
  xlab("Time (hour)") +
  ylab("Electricity (kW)") +
  xlim(c(850,1200))
```
The model does not look very good.



Lets compute the ARIMA RMSE:
```{r}
message("RMSE Predict_ARIMA : ", sqrt(mean((Predict_ARIMA$mean-elec_test)^2)))
```
Predict_ARIMA RMSE: 88.6251889834377
A lower RMSE could be reached by investigating the ACF and PACF.


## NNAR model
```{r}
NNAR_temp_fit <- nnetar(elec_train, xreg = temp_train)
Predict_NNAR_temp <- forecast(NNAR_temp_fit, h=921, xreg = temp_test)

autoplot(elec_train, series = "Train") + 
  autolayer(elec_test, series = "Test set") +
  autolayer(Predict_NNAR_temp$mean, series = "NNAR w/ temperature") +
  ggtitle("Electricity Consumption") +
  xlab("Time (hour)") +
  ylab("Electricity (kW)") +
  xlim(c(850,1200))
```
The model looks good.



Lets compute the NNAR RMSE:
```{r}
message("RMSE Predict_NNAR_temp : ", sqrt(mean((Predict_NNAR_temp$mean-elec_test)^2)))
```
Predict_NNAR_temp RMSE: 53.40427
The NNAR does better than the ARIMA model, so we will choose the NNAR for the power consumption predictions !



## Making the predictions w/ the temperatures

```{r}
temp_forecast <- ts(all_data[4604:4699,3], frequency = 4, start=c(0,1))
NNAR_temp_fit_final <- nnetar(elec, xreg = temp)
Predict_NNAR_temp_final <- forecast(NNAR_temp_fit_final, h=96, xreg=temp_forecast)

autoplot(elec, series = "Electricity Consumption Datas") + 
  autolayer(Predict_NNAR_temp_final$mean,series="Electricity Consumption NNAR Predictions with temperature") +
  ggtitle("Electricity Consumption") +
  xlab("Time (hour)") +
  ylab("Electricity (kW)") +
  xlim(c(850,1200))
```



Exporting the predictions:
```{r}
Predict_NNAR_temp_final$mean
write.xlsx(Predict_NNAR_temp_final$mean, "/Users/tim/Library/CloudStorage/OneDrive-DataScienceTechInstitute/Time Series Analysis (Big Coeff)/Exam/preds_temp.xlsx", sheetName = "Sheet1", col.names = TRUE, row.names = FALSE, append = FALSE)
```



# Comparing the 2 predictions:
```{r}
autoplot(elec, series = "Power Consumption Predictions") + 
  autolayer(Predict_SARIMA_final$mean, series = "SARIMA") +
  autolayer(Predict_NNAR_temp_final$mean, series = "NNAR with Temperature") +
  ggtitle("Electricity Consumption") +
  xlab("Time (hour)") +
  ylab("Electricity (kW)") +
  xlim(c(850,1200))
```
The NNAR with temperatures seems to be more accurate
than the SARIMA model without temperatures.


# Conclusion
The SARIMA model without the temperatures has a RMSE = 57.2087133995781
The NNAR model with the temperatures has a RMSE = 53.40427
Therefore, the best model is the NNAR with the temperatures.
